Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-14 paper.tex
Add wake results to abstract; resolves #52

% Abstract (Less than 200 words)
\abstract{The performance and wake characteristics of cross-flow (often
    vertical-axis) turbines depend on many parameters: solidity, blade profile,
    blade pitch, number of blades, strut drag, operational parameters such as tip
    speed ratio---and Reynolds number. Experiments were performed with a large
    laboratory-scale high solidity cross-flow turbine to investigate Reynolds number
    effects on performance and wake characteristics. It was
    demonstrated that the performance of the cross-flow turbine becomes essentially
    $Re$-independent at a Reynolds number based on turbine diameter of $Re_D \approx
    10^6$, or an approximate Reynolds number based on blade chord of $Re_c \approx 2
    \times 10^5$. A simple model that calculates peak torque coefficient from static
    foil data and cross-flow turbine kinematics was shown to be a reasonable
    estimator for predicting Reynolds number dependence of an actual cross-flow
    turbine operating under dynamic conditions.}

>>>>

% Abstract (Less than 200 words)
\abstract{Experiments were performed with a large laboratory-scale high solidity
    cross-flow turbine to investigate Reynolds number effects on performance and
    wake characteristics, to seek scale thresholds for physical and numerical
    modeling of individual devices and arrays. It was demonstrated that the
    performance of the cross-flow turbine becomes essentially $Re$-independent at a
    Reynolds number based on turbine diameter of $Re_D \approx 10^6$, or an
    approximate Reynolds number based on blade chord of $Re_c \approx 2 \times
    10^5$. A simple model that calculates peak torque coefficient from static foil
    data and cross-flow turbine kinematics was shown to be a reasonable estimator
    for predicting Reynolds number dependence of an actual cross-flow turbine
    operating under dynamic conditions. Mean velocity and turbulence measurements in
    the near-wake showed very subtle differences. However, when transport terms for
    the streamwise momentum and mean kinetic energy were calculated, a similar $Re$
    threshold was revealed. These results imply that physical model studies of
    cross-flow turbines should be $Re_D \sim 10^6$ to properly approximate both the
    performance and wake dynamics of full scale devices and arrays.}
